---
title: "Example Data Checks with `inspectr`"
author: "Jennifer Brussow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Data Checks with inspectr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")

dataset <- data.frame(matrix(NA, 50, 1))

dataset[1] <- c("3462891407", "6042592424", "7702757443", "3373242914", "9553299248", "4327020559", "4087289192", "4322037348", "9770520729", "7824406944", "3062460685", "475410871", "5136035099", "3577493348", "3496003836", "4589950456", "1097854566", "22831223", "1585324323", "8826939308", "544724188", "945814076", "789524583", "2931558249", "6880079016", "KS - Kansas", "4288544351", "21946637157", "499356211", "254377062", "21996327638", "39965152", "2004790709", "5986345268", "2961092736", "4965467175", "1563305976", "225371788", "41210741085", "2015891633", "66528372939", "85020346795", "7522008646", "5259019393", "7113005705", "9792759786", "4606602996", "831670055", "9674734384ï¿½", "5697570341")
colnames(dataset)[1] <- "ID_var"

dataset$FName <- c("Errell", "", "Dorian", "Vivian", "Kaitlynn",  NA, "Dylan", "Randy", "Khalyd", "Paul", "CLAYTON", "David", "Joslyn", "Aspen", "Tyreek", "Aerielle", "Jena", "Caden", "Tashina", "Keonna", "Heather", "Jude", "Brandon", "Devin", "Ryan", "Silas", "Carmine", "Hassan", "Ozmond", "Caden",  "Stuart", "Marlayni", "Anthony", "Jaylen", "Kendal", "Nadia", "Alicia", "JOSHUA", "JAVON",  "MADELYN",   "KENDALL", "WILLIAM", "Gabriel", "Chloe", "Jordyn", "Brian", "Fatima", "Jonathan", "Jacob", "Cesar")

dataset$Var1 <- c(seq(1, 100, 2))
dataset$Var2 <- c(seq(2, 100, 2))

dataset[23, "Var2"] <- 4
dataset[14, "Var1"] <- 56
dataset[7, "Var1"] <- 14
dataset[9, "Var2"] <- 17

dataset$Perf_Lvl <- c(rep("Basic", 8), NA, NA, rep("Basic", 8),
                      rep("Intermediate", 6), NA, rep("Intermediate", 6),
                      "BAsic", rep("Advanced", 18))

```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```


