---
title: "Example Data Checks with `inspectr`"
author: "Jennifer Brussow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Data Checks with inspectr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Format of the Package
The `inspectr` package is designed to perform basic data checks without the user needing to understand the intricacies of apply functions.

The functions can be grouped into two categories: column checks and
basic fidelity checks.

#### Column check functions
These are the basic functions used to perform checks. Each function checks one column for data fidelity, and functions exist to check that column against one or two additional columns. A data frame and a column name (or names) go in; a filtered set of records exhibiting issues comes out (either as a dataframe or as an .xlsx document - your choice!)

#### Basic fidelity check functions
These functions are designed to be used with the column check functions. They perform basic checks on the data, like ensuring that all data in a column are of the same type or ensuring that all values in column 1 are less than their corresponding values in column 2.


## Checking an example dataset
To illustrate how to use these functions, we'll apply some basic checks to a sample dataset:
```{r echo = FALSE}
knitr::kable(dataset, format = "markdown", align = "l", row.names = FALSE)
```


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```


